---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# servermonks

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/servermonks)](https://CRAN.R-project.org/package=servermonks)
<!-- badges: end -->

## Purpose

The goal of servermonks is to compare COVID-19 vaccination data for California with the results, by county, of the 2021 CA Gubernatorial Recall Election. In [a CNN article](https://www.cnn.com/2021/08/28/politics/california-recall-what-matters/index.html) analyzing the context behind the recall election, Ethan Cohen (Reston and CNN) is quoted saying that:

"[Although political groups in CA launched efforts to oust Gov. Newsom before the pandemic, the]quest to collect enough signature petitions to force a recall election took off late last year amid anger about Newsom’s Covid-19 stay-at-home orders and other restrictions. And while the governor appeared to be in a strong position to withstand the effort for much of this year, the resurgence of the pandemic [with the delta variant] and frustration with the state’s wildfire, drought and homelessness crises has injected an unexpected level of volatility into the race in an overwhelmingly blue state."

The functions and tidy datasets included in this package will thus empower users to ask questions about the different ways in which counties in California have responded to the pandemic.

## Target audiences:

Public and private entities who are interested in looking at a relationship, if any, between trends in the polarized political races we saw during the course of the pandemic 


## Installation

You can install the development version of servermonks from Github with the following code:

```{r}
# install.packages("devtools")
devtools::install_github("zbaker23/server-monks")
```

## Example

This is a basic example which shows you how to use the print() base R function within our servermonks package to visualize the ballot_question dataset. For the ballot measure question of, "Shall Gavin Newsom Be Recalled (Removed) From the Office of Governor?" for the 2021 CA Gubernational Recall Election, this dataset details the number of "yes" votes, the number of "no" votes, the percentage of the votes that are "yes", and the percentage of the votes that are "no" by county. 

```{r example}

library(servermonks)

print(ballot_question)

```

## Group assignment

For Project Phase III, we want to continue working with the servermonks package to include further functions that will help users summarize and then view the built-in datasets for our package in different ways. The current function in our package, quick_summary_vaxx_vs_recall(), lets a user quickly look statistics on vaccine rates and support for the 2021 recall election in a county of their choice, and compare them to the California counties with the most extreme statistics for vaccination rates and recall support. We plan to write a function that creates visualizations allowing users to easily compare counties to each other, rather than only returning descriptive text. 


```
