---
title: "function"
author: "Jane Andrews"
date: "2022-11-22"
output: html_document
---

## Function

### Description

**Purpose**

### The purpose of this function, quick_summary_vaxx_vs_recall() is to allow a user to quickly find out information about the rates of full vaccinations and the support for the 2021 attempted recall of Gov. Gavin Newsom in a county of their chosing. As the function supplies the user with information about the state's extremes (i.e. highest and lowest rates of vaccination, highest and lowest levels of support for Gavin Newsom's recall), using this function quickly informs a reader of California's political diversity, and gives them a better understanding of where a county of their choice may fall on the state's political spectrum. The recall efforts were, in part, an expression of opposition to Gov. Newsom's strict COVID-19 policies, and yet these data are not often explored side by side, even though comparison is useful. A potential user for this may be someone who is looking for information about the county they live in, or a county they may want to move to, or travel to, to get a quick view of what the attitudes toward COVID-19 policies may be. 

**Dependencies/Setup**

```{r}
library(servermonks)

data("ballot_question")
data("vaxx_counties")
```

**Arguments**

### the function takes one argument, yourcounty, which is a string describing the name of the county a user is asking for information on. yourcounty should be capitalized, and the word "County" should not appear in the string. For example, if you are looking for information on Los Angeles County, yourcounty = "Los Angeles".

**Result**

### The function returns a short paragraph informing the user of the highest and lowest county vaccination levels in California, the highest and lowest levels of support for Gavin Newsom's recall by county, and information on the levels of vaccination and recall support in the county they have requested information about. 

### Code
```{r}
quick_summary_vaxx_vs_recall <- function(yourcounty) {

most_support_recall <- ballot_question %>%
  arrange(desc(yes_per)) %>%
  head(1) 

most_support_recall <- as.character(most_support_recall["county"])

current_date <- vaxx_counties %>%
  filter(administered_date == "2022-11-14") 

least_vaxxed <- vaxx_counties %>%
  filter(administered_date == "2022-11-14") %>%
  mutate(pervaxxed = cumulative_booster_recip_count/booster_eligible_population) %>%
  arrange(pervaxxed) %>%
  head(1)

least_vaxxed <- as.character(least_vaxxed["county"])

least_support_recall <- ballot_question %>%
  arrange(yes_per) %>%
  head(1) 

least_support_recall <- as.character(least_support_recall["county"])
  
most_vaxxed <- vaxx_counties %>%
  filter(administered_date == "2022-11-14") %>%
  mutate(pervaxxed = cumulative_booster_recip_count/booster_eligible_population) %>%
  arrange(desc(pervaxxed)) %>%
  head(1)

most_vaxxed <- most_vaxxed["county"]

most_vaxxed<- as.character(most_vaxxed)

highest_vaxx_rate <- vaxx_counties %>%
  filter(administered_date == "2022-11-14") %>%
   mutate(pervaxxed = (cumulative_booster_recip_count/booster_eligible_population)*100) %>%
  arrange(desc(pervaxxed)) %>%
  head(1) %>%
  mutate(reformat_pervaxxed = substring(as.character(pervaxxed), 1, 5))

highest_vaxx_percent <- as.character(highest_vaxx_rate["reformat_pervaxxed"])

lowest_vaxx_rate <- vaxx_counties %>%
  filter(administered_date == "2022-11-14") %>%
   mutate(pervaxxed = (cumulative_booster_recip_count/booster_eligible_population)*100) %>%
  arrange(pervaxxed) %>%
  head(1) %>%
  mutate(reformat_pervaxxed = substring(as.character(pervaxxed), 1, 5))

lowest_vaxx_percent <- as.character(lowest_vaxx_rate["reformat_pervaxxed"])

highest_recall_notsupport <- ballot_question %>%
  arrange(desc(yes_per)) %>%
  head(1) %>%
  mutate(highest_pernotsupport = as.character(no_per *100))

highest_recall_notsupport_percent <- as.character(highest_recall_notsupport["highest_pernotsupport"])

lowest_recall_notsupport <- ballot_question %>%
  arrange(yes_per) %>%
  head(1) %>%
  mutate(lowest_pernotsupport = as.character(no_per *100))

lowest_recall_notsupport_percent <- as.character(lowest_recall_notsupport["lowest_pernotsupport"])

yourcounty_vaxx_rate <- vaxx_counties %>%
  filter(administered_date == "2022-11-14") %>%
  filter(county == yourcounty) %>%
  mutate(pervaxxed = (cumulative_booster_recip_count/booster_eligible_population)*100) %>%
  mutate(reformat_pervaxxed = substring(as.character(pervaxxed), 1, 5))

reformat_pervaxxed <- as.character(yourcounty_vaxx_rate["reformat_pervaxxed"])

yourcounty_recall_notsupport <- ballot_question %>%
  filter(county == yourcounty) %>%
  mutate(reformat_pernotsupport = as.character(no_per *100))

yourcounty_recall_notsupport <- as.character(yourcounty_recall_notsupport["reformat_pernotsupport"])

paste(most_support_recall, "County had the highest share of voters supporting Gov. Gavin Newsom's recall of all California counties, with", lowest_recall_notsupport_percent, "percent of voters supporting the recall.", least_support_recall, "County had the lowest share of voters supporting Gov. Gavin Newsom's recall of all California counties, with", highest_recall_notsupport_percent, "of voters voting for the recall. As of November 14, 2022,", least_vaxxed, "County has the lowest share of residents fully vaccinated of all California counties, with", lowest_vaxx_percent, "of residents fully vaccinated.", most_vaxxed, "County is the most fully vaccinated county in California, with", highest_vaxx_percent, "of residents fully vaccinated.", "In comparison,", yourcounty, "County has a full vaccination rate of", reformat_pervaxxed, "percent and", yourcounty_recall_notsupport, "percent of voters voted against Gavin Newsom's recall.") }
```

### Examples

> Give 2-3 examples of typical usage of your function. Describe in words what is being illustrated.
This shows a few examples of summary paragraphs that could be generated for different counties a user may choose. 

```{r ex1}
quick_summary_vaxx_vs_recall("Los Angeles")
quick_summary_vaxx_vs_recall("Orange")
quick_summary_vaxx_vs_recall("San Mateo")
quick_summary_vaxx_vs_recall("Sonoma")
```

```{r}
quick_summary_vaxx_vs_recall("Alpine")
quick_summary_vaxx_vs_recall("Lake")
quick_summary_vaxx_vs_recall("Contra Costa")
```


### Testing

```{r}

library(testthat)
expect_equal(quick_summary_vaxx_vs_recall("Alpine"), "Lassen County had the highest share of voters supporting Gov. Gavin Newsom's recall of all California counties, with 86.1 percent of voters supporting the recall. San Francisco County had the lowest share of voters supporting Gov. Gavin Newsom's recall of all California counties, with 15.8 of voters voting for the recall. As of November 14, 2022, Merced County has the lowest share of residents fully vaccinated of all California counties, with 40.10 of residents fully vaccinated. San Francisco County is the most fully vaccinated county in California, with 77.04 of residents fully vaccinated. In comparison, Alpine County has a full vaccination rate of 44.04 percent and 61.1 percent of voters voted against Gavin Newsom's recall.")
expect_equal(quick_summary_vaxx_vs_recall("Lake"), "Lassen County had the highest share of voters supporting Gov. Gavin Newsom's recall of all California counties, with 86.1 percent of voters supporting the recall. San Francisco County had the lowest share of voters supporting Gov. Gavin Newsom's recall of all California counties, with 15.8 of voters voting for the recall. As of November 14, 2022, Merced County has the lowest share of residents fully vaccinated of all California counties, with 40.10 of residents fully vaccinated. San Francisco County is the most fully vaccinated county in California, with 77.04 of residents fully vaccinated. In comparison, Lake County has a full vaccination rate of 53.97 percent and 51 percent of voters voted against Gavin Newsom's recall.")
expect_equal(quick_summary_vaxx_vs_recall("Contra Costa"), "Lassen County had the highest share of voters supporting Gov. Gavin Newsom's recall of all California counties, with 86.1 percent of voters supporting the recall. San Francisco County had the lowest share of voters supporting Gov. Gavin Newsom's recall of all California counties, with 15.8 of voters voting for the recall. As of November 14, 2022, Merced County has the lowest share of residents fully vaccinated of all California counties, with 40.10 of residents fully vaccinated. San Francisco County is the most fully vaccinated county in California, with 77.04 of residents fully vaccinated. In comparison, Contra Costa County has a full vaccination rate of 67.30 percent and 71.4 percent of voters voted against Gavin Newsom's recall.")
```

